Trajectories: how functional traits influence plant growth and shade tolerance across the life-cycle

### 2017-08-09 ms/ms-common-defs.tex
Incorporate suggestions from R Duursma throughout article
minor edits, address change

\title{Growth trajectories: how functional traits influence plant growth}
\runninghead{H\lowercase{ow traits influence growth}}

\author{Daniel S. Falster\textsuperscript{1,\textasteriskcentered}, Remko Duursma\textsuperscript{2}, \& Richard G. FitzJohn\textsuperscript{1,3}}
\affiliation{\textsuperscript{1} Biological Sciences, Macquarie University NSW 2109, Australia \\
\textsuperscript{2} Hawkesbury Institute for the Environment, Western Sydney University, Locked Bag 1797, Penrith NSW 2751, Australia \\
\textsuperscript{3} Imperial College, London, United Kingdom \\
\textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{adaptive.plant@gmail.com}
}

>>>>

\title{Trajectories: how functional traits influence plant growth and shade tolerance across the life-cycle}
\runninghead{H\lowercase{ow traits influence growth}}

\author{Daniel S. Falster\textsuperscript{1,\textasteriskcentered}, Remko A. Duursma\textsuperscript{2}, \& Richard G. FitzJohn\textsuperscript{3}}
\affiliation{\textsuperscript{1} Evolution \& Ecology Research Centre, School of Biological, Earth and
Environmental Sciences, University of New South Wales, Sydney, NSW 2052, Australia \\
\textsuperscript{2} Hawkesbury Institute for the Environment, Western Sydney University, Locked Bag 1797, Penrith NSW 2751, Australia \\
\textsuperscript{3} Imperial College, London, United Kingdom \\
\textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{adaptive.plant@gmail.com}
}
